The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
fixed typo.
future work bullets expanded

\makeatletter
\setlength{\@fptop}{0pt}1
\setlength{\@fpbot}{0pt}
\setlength{\@fpsep}{0pt}
\makeatother

@@

There are several avenues for future work, including
\begin{itemize}
\item detailed comparison to specific experimental apparatus. will gle dynamics be visible? 
\item the vertical dimension is incompletely modeled - stratification, etc
\item explore saturation property dependence of system on rotation profile 
\item different field geometries (e.g. radially varying)
\item other radial boundary conditions
\item drop axisymmetry
\item comparison to simulation in both weakly and strongly nonlinear regimes
\end{itemize}

\section{Acknowledgements}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-11-44155. J.S.O. acknowledges support from NASA grant 15-LWS15\_2-0063. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, Ellen Zweibel, etc for useful discussion.

>>>>

\makeatletter
\setlength{\@fptop}{0pt}
\setlength{\@fpbot}{0pt}
\setlength{\@fpsep}{0pt}
\makeatother

@@

We detail several avenues for future work, which highlight the application of this theory to both laboratory experiments and astrophysical disks.

\begin{itemize}
\item This theory may be applied to a specific experimental apparatus to model the predicted saturated state. One can then ask whether GLE dynamics should be detectable, especially over apparatus-driven flows.
\item The saturation properties of different rotation profiles may be compared by direct application of the theory developed here.
\item Vertical stratification may be added to the base state, which would be a more realistic model of global vertical disk structure. 
\item Other nonideal MHD effects such as the Hall effect and ambipolar diffusion may be straightforwardly added to this model, and are of particular interest for modeling protoplanetary disks. 
\item The background magnetic field geometry may be generalized to include radial variation.
\item The radial boundary conditions considered here may be expanded to mimic astrophysical disks rather than TC devices.
\item This theory may be compared to simulations in both the weakly and strongly nonlinear regimes. 
\end{itemize}

\section{Acknowledgments}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-11-44155. J.S.O. acknowledges support from NASA grant 15-LWS15\_2-0063. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, Ellen Zweibel, etc for useful discussion.
